### 2017-12-12 readme.rmd
minor wording

I next color coded the results by significance, assessed as a posterior probability &ge; `r pp_thresh`. This is a low threshold, most Bayesian phylogenetic studies apply a more stringent (higher) threshold to assess significance. The significance of the results is presented below in Figure 3.

@@

The work of Feuda *et al.* 2017 provides an enticing peek at a portion of this landscape, but without broader context still fails to allow us to come to strong conclusions. Exploring additional sensitivity will help us understand this bigger picture. In this sense, sensitivity is an asset rather than a liability.

@@

I think that the rigorously blocked approach that Feuda *et al.* 2017 very exciting and the way of the future. It can provide a clear picture of the support landscape as it depends on different factors and their interactions. We need to expand this approach.

>>>>

I next color coded the results by significance, assessed as a posterior probability &ge; `r pp_thresh`. This is a low threshold. Most Bayesian phylogenetic studies apply a more stringent (higher) threshold to assess significance. The significance of the results is presented below in Figure 3.

@@

The work of Feuda *et al.* 2017 provides an enticing glimpse at a portion of this landscape, but without broader context still fails to allow us to come to strong conclusions. Exploring additional sensitivity will help us understand this bigger picture. In this sense, sensitivity is an asset rather than a liability.

@@

I think that the rigorously blocked approach of Feuda *et al.* 2017 is very exciting and the way of the future. It can provide a clear picture of the support landscape as it depends on different factors and their interactions. We need to expand this approach.
